---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickstats

The goal of quickstats is to save some time while doing basic data anaysis with DPLYR

## Installation

You can install the released version of quickstats from [Github](https://github.com/despresj/quickstats) with:

``` r
install.packages("devtools")

devtools::install_github("despresj/quickstats")
```
```{r library}
library(quickstats)
```

## Examples

Return a tibble tailored to non-statisticans attempting to maximizing their understanding of their data
```{r basicsummary}
stats_presentable(mtcars, mpg, cyl)
```

This tibble that gives a quick summary of the data
```{r basicpresentable}
stats_summary(mtcars, mpg, cyl)
```

Adjust the rounding
```{r adj-round}
stats_presentable(mtcars, mpg, rounding_digits = 5)
```

Use two grouping variables
```{r two-groups}
stats_summary(mtcars, mpg, am, rounding_digits = 5)
```

Using the notin operator
```{r}
dplyr::filter(mtcars, carb %!in% c(1,2,3))
```

